NURM: a tool to locate numerical differences in pipelines

### 2019-05-27 paper.tex
More edits

\subsection{Subject types}

@@

  \State /* Input: - a list of n trees; \texttt{T = [t${_1}$, t${_2}$,...,t${_n}$]}
  \State /*\quad \quad \quad \quad - a distance threshold value; \texttt{threshold}
  \State /* Output: a list of clusters; \texttt{C = [c${_1}$,c${_2}$,...,c${_k}$]}
  \State \texttt{\# Create a cluster for each tree in input list;}
  \State \texttt{C = [t${_1}$, t${_2}$,...,t${_n}$]}
  \State \texttt{\# Define a 2 $\times$ 2 array to store distances}
  \State \texttt{D} = \texttt{array(n, n)}
  \While{\texttt{len(C)} > \texttt{1}}  
  \State \texttt{\# Select the two nearest clusters}
  \For{\texttt{i=1} to \texttt{n}}
  \For{\texttt{j=i+1} to \texttt{len(C)}}
  \State \texttt{D[i][j]} = \texttt{edit\_distance(C[i], C[j])}
    \EndFor
  \EndFor
  \State \texttt{i, j} = $\argmin \left\{ \texttt{D[i][j]}, \ \texttt{i, j} \in \llbracket 1, \texttt{len(C)}\rrbracket^2 \right\}$
  \If{\texttt{D[i][j]} > \texttt{threshold}}
  \State \Return \texttt{C}
  \Else
  \State \texttt{\# Merge C[j] into C[i]}
  \State \texttt{C[i]} = \texttt{merge}(\texttt{C[i] and C[j]})
  \State \texttt{\# Remove C[j] from C}
  \State \texttt{remove(C[j], C)}
  \EndIf
  \EndWhile
%  \State Function edit\_distance (C${_1}$, C${_2}$)
%  \State EndFunction
\end{algorithmic}
\end{algorithm}

@@

NURM-tool labels the processes into four 
categories based on the process tree and the \textit{difference} JSON file 
mentioned in the previous sections:
\begin{enumerate}
\item Processes that read and write files that do not have differences 
are \emph{transparent} (Figure~\ref{fig:processes}.a).
\item Processes that read files 
that do not have any differences but write files that have differences 
\emph{create} differences in the pipeline (Figure~\ref{fig:processes}.b).
\item Processes that read files 
that have differences and write files that do not have differences \emph{remove} 
differences from the pipeline (Figure~\ref{fig:processes}.c).
\item Processes that read files that have differences and write files that 
also have differences are 
\emph{unknown} (Figure~\ref{fig:processes}.d).
\end{enumerate}

\begin{figure}%\centering
\centering
    \begin{subfigure}{0.4\linewidth}
        \includegraphics[scale=0.34]{images/green.png}
        \caption{Transparent}
        \label{fig:green}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.4\linewidth}
    \includegraphics[scale=0.34]{images/red.png}
    \caption{Creates differences}
    \label{fig:red}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.4\linewidth}
    \includegraphics[scale=0.34]{images/blue.png}
    \caption{Removes differences}
    \label{fig:blue}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.4\linewidth}
    \includegraphics[scale=0.34]{images/yellow.png}
    \caption{Unknown}
    \label{fig:yellow}
\end{subfigure}
    \caption{Different type of classified process based on the input/output files.
  Dashed edges refer to the file dependencies between processes A and B 
  if a file written by A is read by B. Solid black edges refer to the 
  relationship between parent and child processes.}
    \label{fig:processes}
\end{figure}

There are some issues that should be addressed to label process 
properly, including capturing temporary files that have been removed 
during the execution, capturing files written by multiple processes, 
and unknown process.

\subsubsection{Capture temporary files} 
The labelling of processes that read or 
write temporary files is uncertain when these files are deleted during 
the execution. To address this issue, we replace every process P that 
writes temporary files with a modification of P that first calls P and 
then backs up all its output files to a read-only directory. This 
replacement is done by modifying the Unix PATH variable to point to a 
directory containing the modified versions of the processes. This 
solution does not cover the temporary files that are removed by P 
itself; this is not a problem since these files do not play any role in 
the subsequent steps of the pipeline, by definition.

\subsubsection{Capture multiple write files} 
Files written by multiple processes also lead 
to unknown labels. To address this issue for a file F 
written by processes in \textbf{P} = \{$P_{1}$, \ldots $P_{n}$\}, we 
(1) check that processes in \textbf{P} do not write concurrently to F, 
(2) we establish an order on \textbf{P} based on the creation timestamp 
of the processes, (3) we replace ever process $P_{i}$ in \textbf{P} by 
a wrapper that first calls $P_{i}$ and then backs up F to a read-only 
directory. Thus, multiple versions of F are saved and used in the 
analysis.

>>>>

\subsection{Subject clustering}

@@

  \State /* Input: - a list of n trees; \texttt{T = [t${_1}$, t${_2}$,...,t${_n}$]}
  \State /*\quad \quad \quad \quad - a distance threshold value; \texttt{threshold}
  \State /* Output: a list of clusters; \texttt{C = [c${_1}$,c${_2}$,...,c${_k}$]}
  \State \texttt{\# Create a cluster for each tree in input list;}
  \State \texttt{C = [t${_1}$, t${_2}$,...,t${_n}$]}
  \State \texttt{\# Define a 2 $\times$ 2 array to store distances}
  \State \texttt{D} = \texttt{array(n, n)}
  \While{\texttt{len(C)} > \texttt{1}}  
  \State \texttt{\# Select the two nearest clusters}
  \For{\texttt{i=1} to \texttt{n}}
  \For{\texttt{j=i+1} to \texttt{len(C)}}
  \State \texttt{D[i][j]} = \texttt{edit\_distance(C[i], C[j])} \tristan{how do you define the distance between two clusters?}
    \EndFor
  \EndFor
  \State \texttt{i, j} = $\argmin \left\{ \texttt{D[i][j]}, \ \texttt{i, j} \in \llbracket 1, \texttt{len(C)}\rrbracket^2 \right\}$
  \If{\texttt{D[i][j]} > \texttt{threshold}}
  \State \Return \texttt{C}
  \Else
  \State \texttt{\# Merge C[j] into C[i]}
  \State \texttt{C[i]} = \texttt{merge}(\texttt{C[i] and C[j]})
  \State \texttt{\# Remove C[j] from C}
  \State \texttt{remove(C[j], C)}
  \EndIf
  \EndWhile
%  \State Function edit\_distance (C${_1}$, C${_2}$)
%  \State EndFunction
\end{algorithmic}
\end{algorithm}

\tristan{how do you choose the representative process graph in each cluster?}

@@

We label in four categories the processes of the representative graph of each subject:
\begin{enumerate}
\item Processes that read files that do not have differences and write files that do not have differences 
are labeled \emph{transparent} (Figure~\ref{fig:processes}.a).
\item Processes that read files 
that do not have differences but write files that have differences 
\emph{create} differences (Figure~\ref{fig:processes}.b).
\item Processes that read files 
that have differences and write files that do not have differences \emph{remove} 
differences (Figure~\ref{fig:processes}.c).
\item Processes that read files that have differences and write files that 
also have differences are called
\emph{undetermined} (Figure~\ref{fig:processes}.d).
\end{enumerate}

\begin{figure}%\centering
\centering
    \begin{subfigure}{0.4\linewidth}
        \includegraphics[scale=0.34]{images/green.png}
        \caption{Transparent}
        \label{fig:green}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.4\linewidth}
    \includegraphics[scale=0.34]{images/red.png}
    \caption{Creates differences}
    \label{fig:red}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.4\linewidth}
    \includegraphics[scale=0.34]{images/blue.png}
    \caption{Removes differences}
    \label{fig:blue}
    \end{subfigure}
    \hfill
    \begin{subfigure}{0.4\linewidth}
    \includegraphics[scale=0.34]{images/yellow.png}
    \caption{Undetermined}
    \label{fig:yellow}
\end{subfigure}
    \caption{Different type of classified process based on the input/output files.
  Dashed edges refer to the file dependencies between processes A and B 
  if a file written by A is read by B. Solid black edges refer to the 
  relationship between parent and child processes.}
    \label{fig:processes}
\end{figure}

Undetermined processes are due to temporary files, and files that were
written by more than a single process. In both situations, breakpoints must
be added to the pipeline to capture intermediary file states and label
undetermined processes.

\subsubsection{Capturing temporary files}

The labelling of processes that read or 
write temporary files is undetermined because these files are deleted during 
the execution. To address this issue, we replace in Condition 1 every process P that 
writes temporary files with a modification of P that first calls P and then
backs up all its output files to a read-only directory. This replacement is
done by modifying the PATH environment variable to point to a directory
containing a modified version of the executable called by the process. The
modified executable will run the original executable and then backup its
output files. \tristan{Add an example modified script (listing), and replace input checks on file names by checksums.}
This 
solution does not cover the temporary files that are removed by P 
itself, but this is not a problem since these files do not play any role in 
the subsequent steps of the pipeline.

\subsubsection{Capturing multiple write files}

Files written by multiple processes also lead 
to unknown labels. To address this issue for a file F 
written by processes in \textbf{P} = \{$P_{1}$, \ldots $P_{n}$\}, we 
(1) check that processes in \textbf{P} do not write concurrently to F, 
(2) we establish an order on \textbf{P} based on the creation timestamp 
of the processes, (3) we replace ever process $P_{i}$ in \textbf{P} by 
a wrapper that first calls $P_{i}$ and then backs up F to a read-only 
directory. Thus, multiple versions of F are saved and used in the 
analysis.
